---
title: "DA2 - Assingment 1" 
author: "Oszkar"
date: "11/27/2021"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(fixest)

df <- read_csv("https://raw.githubusercontent.com/oegervari/Data_analysis_2/main/data/morg-2014-emp.csv")

df <- df %>% filter(occ2012 == 800) %>% filter(earnwke > 50) %>% mutate(occupation = 'Accountants and auditors')

```

## Introduction

In this assignment I examine the gender wage gap difference in the [cps-earningsdatase](https://osf.io/g8p9j/) dataset. First I take a look at the unconditional gender gap, then I will attempt to how how the gender gap varies with the level education.

From the dataset I chose the 'Accountants and auditors' profession with occupation code 800.


## Unconditional gender gap

```{r, echo=F}
feols( earnwke ~ sex , data = df )
```

The table shows us that the Intercept is 1757.979, which in this case means the expected male weekly earnings. The coefficient 'sex' has a value of -338.624, which means that females are expected to earn less than males by this amount. The t values of the coefficients are very small, which means that the probability that the observed wage gap difference between sexes is due to chance, is unlikely. 
The adjusted R2 score of this model is around 0.06, which means that 6% of the wage difference is explained by sex.

```{r, echo=F}
ggplot(data = df, aes(x = sex, y = earnwke)) +
  geom_point()+ 
  geom_smooth(method="lm")+
  scale_x_continuous(limits=c(1, 2),     breaks= seq(1, 2, by=1))
```







